\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-05-16 cover-letter/cover-letter.Rmd
tweak cover letter

We have included a new subsection "2.4 Reasons to use calendar-based graphics" to explain why calendar displays are useful and when to use them, and a new section "3 Making calendar facets" to describe a new calendar faceting method `facet_calendar()`, that extends **ggplot2** intervals and complements the existing function `frame_calendar()`.

We have provided a detailed response letter to reviewers, as attached.

>>>>

The major changes include two new sections: a subsection "2.4 Reasons to use calendar-based graphics" to explain why calendar displays are useful and when to use them, and a section "3 Making calendar facets" to describe a new calendar faceting method `facet_calendar()`, that extends **ggplot2** intervals and complements the existing function `frame_calendar()`.

A detailed response letter to reviewers has been provided.
